Visualizing probability distributions across bivariate cyclic temporal granularities

### 2021-05-16 main.Rmd
The term “time instants” briefly described

\begin{defn}\label{def:definition}
A \textbf{time domain} is a pair $(T; \le)$ where $T$ is a non-empty set of time instants and $\le$ is a total order on $T$.
\end{defn}

>>>>

\begin{defn}\label{def:definition}
A \textbf{time domain} is a pair $(T; \le)$ where $T$ is a non-empty set of time instants (equivalently, moments or points) and $\le$ is a total order on $T$.
\end{defn}
